Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-05-20 article.tex
Pointer for writing
Add some notation
wording

% BG : brain, complex organ

Understanding how the brain works is a key to understand and to treat
brain pathologies and disorders such as Parkinson's disease, epilepsy.
Retrieving the connectomes, neurons connectivity map, will shed new lights on
the anatomical and functional connectivity of the brain.
The human brain is a complex biological organ, which is formed by 100
billions of neurons with 7000 synaptic connections on average. Inferring the
neuron connectivity network through dissection would be an impossible
and daunting task.

% Issue : we have data, but need to have to infer the connectome
Cutting edge optical devices (TODO CITE) allows to track simultaneously
the neural activity of thousands of neurons through the fluorescent
calcium indicator. The neuron connectivity network could be inferred
from those neuron activity signals.

@@

>>>>

% BG : brain, complex organ
Understanding how the brain works is a key to understand and to treat
brain pathologies and disorders such as Parkinson's disease, epilepsy.
Retrieving the connectomes, neurons connectivity map, will shed new lights on
the anatomical and functional connectivity of the brain.
The human brain is a complex biological organ, which is formed by 100
billions of neurons with 7000 synaptic connections on average. Inferring the
neuron connectivity network through dissection would be an impossible
and daunting task.

% Issue : we have data, but need to have to infer the connectome
% TODO Shed light on the difficulty of the inverse problem:
% noise, time scale (optical imaging speed vs neuron speed), decay of
% fluorescent signal.
Cutting edge optical devices (TODO CITE) allows to track simultaneously
the neural activity of thousands of neurons through the fluorescent
calcium indicator. The neuron connectivity network could be inferred
from those neuron activity signals.

@@

% Introduce notation + goal in mathematical score
Given $X \in \mathcal{R}^{n \times p}$  a set of $p$ time series of fluorescent
calcium concentration of size $n$ from $p$ neurons, the goal is to infer the
connectivity network $y \in \left\{0, 1\right\}^{p \times p}$ where
non zero values indicate that the neuron $i$ have an outward connection to
the neuron $j$.

% Introduce partial correlation
% Introduce directivity
% Introduce filtering
